Scottish Child Payment Interventions

### 2024-01-20 minos/outcomes/CPR_vis.Rmd
Added more to CPR vis script and added a missing argument to some function calls in SCP vis

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'scaled_scotland')

@@

@@

@@

```{r, echo=FALSE}
threshold <- base %>%
  select(time, weight, hh_income) %>%
  group_by(time) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')

threshold <- base %>%
  select(time, weight, run_id, hh_income) %>%
  group_by(time, run_id) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
  group_by(time) %>%
  summarise(poverty_threshold_mean = mean(poverty_threshold),
            lower = min(poverty_threshold),
            upper = max(poverty_threshold))

ggplot(data = threshold, aes(x = time, y = poverty_threshold_mean)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge') +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

@@

>>>>

```{r read_data}
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')

@@

int.list <- list(base, int)
scen.list <- c('base', 'ChildPovReduction')

@@

```{r SF12_deciles}
SF12.by.simd.deciles <- function(df.list, scen.list, start.year = 2020, batch=FALSE) {
  single.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }
  batch.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, run_id, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile, run_id) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }

  if (batch) {
    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
  } else {
    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile'))
  }

  combined$simd_decile <- as.factor(combined$simd_decile)

  int.labels <- scen.list[-1]

  for (int in int.labels) {
    int.name <- paste0(int, '.SF12')
    if (batch) {
      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
        geom_smooth(aes(y = base.SF12)) +
        geom_smooth(aes(y = .data[[int.name]]), linetype='dashed') +
        labs(title = 'SF12 MCS Deciles', subtitle = paste0('Baseline vs ', int)) +
        xlab('Year') +
        ylab('Difference')
    } else {
      p1 <- ggplot(combined, aes(x = time, group = simd_decile, colour = simd_decile)) +
        geom_line(aes(y = base.SF12)) +
        geom_line(aes(y = .data[[int.name]]), linetype='dashed') +
        labs(title = 'SF12 MCS Deciles', subtitle = int) +
        xlab('Year') +
        ylab('Difference')
    }
    print(p1)
  }
}
```

```{r SF_change_deciles, echo=FALSE}
SF12.change.by.deciles <- function(df.list, scen.list, start.year = 2020, batch = FALSE) {
  single.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }
  batch.mean <- function(data, scen, start.year) {
    newvar.name <- paste0(scen, '.SF12')
    data <- data %>%
      select(time, weight, simd_decile, run_id, SF_12) %>%
      filter(time >= start.year) %>%
      group_by(time, simd_decile, run_id) %>%
      summarise(!!sym(newvar.name) := weighted.mean(SF_12, w = weight))
    return(data)
  }

  if (batch) {
    mod.list <- mapply(batch.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile', 'run_id'))
  } else {
    mod.list <- mapply(single.mean, int.list, scen.list, start.year, SIMPLIFY = FALSE)
    combined <- mod.list %>%
      reduce(full_join, by=c('time', 'simd_decile'))
  }

  combined$simd_decile <- as.factor(combined$simd_decile)

  # List of intervention columns
  int_cols <- grep("ChildPovReduction.SF12", names(combined), value = TRUE)

  # Create the new dataframe with differences
  combined <- combined %>%
    mutate(across(all_of(int_cols), ~ . - base.SF12, .names = "diff{col}")) %>%
    select(time, simd_decile, starts_with("diff")) %>%
    rename_with(~ str_replace_all(., "diffint(\\d+).SF12", "diff\\1"))

  combined <- combined %>%
    pivot_longer(cols = starts_with('diff'),
                 names_to = 'scen',
                 values_to = 'diff')

  if (batch) {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_smooth() +
      geom_hline(yintercept = 0, linetype='dashed') +
      facet_wrap(. ~ scen, ncol=1) +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  } else {
    p1 <- ggplot(combined, aes(x = time, y = diff, group = simd_decile, colour = simd_decile)) +
      geom_line() +
      geom_hline(yintercept = 0, linetype='dashed') +
      facet_wrap(. ~ scen, ncol=1) +
      labs(title = 'Relative change in SF12 MCS', subtitle = 'Whole population') +
      xlab('Year') +
      ylab('Difference')
  }

  ggsave(filename = 'test_plot.png',
         plot = p1,
         path = here::here('plots', 'SCOTGOVWORK'),
         width = 9,
         height = 20)

  print(p1)
}
```

@@

```{r, echo=FALSE}
if (batch) {
  threshold <- base %>%
  select(time, weight, run_id, hh_income) %>%
  group_by(time, run_id) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6)) %>%
  group_by(time) %>%
  summarise(poverty_threshold_mean = mean(poverty_threshold),
            lower = min(poverty_threshold),
            upper = max(poverty_threshold))

ggplot(data = threshold, aes(x = time, y = poverty_threshold_mean)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge') +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
} else {
  threshold <- base %>%
  select(time, weight, hh_income) %>%
  group_by(time) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  geom_hline(yintercept = rel.pov.threshold, linetype='dashed') +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
}
```

@@

## DECILES

```{r}
SF12.by.simd.deciles(int.list, scen.list, start.year = 2020, batch = batch)
```

```{r}
SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = batch)
```

```{r}
SF12.change.by.deciles(int.list, scen.list, start.year = 2020, batch = batch)
```

### 2024-01-20 minos/outcomes/SCP_vis.Rmd
Added more to CPR vis script and added a missing argument to some function calls in SCP vis

```{r}
SF12.by.simd.deciles(int.list, scen.list)
```

```{r}
SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = FALSE)
```

@@

```{r}
SF12.change.by.deciles(int.list, scen.list)
```

@@

SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic')
SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one')
SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children')
SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')

>>>>

```{r}
SF12.by.simd.deciles(int.list, scen.list, batch = batch)
```

```{r}
SF12.by.simd.deciles(int.list, scen.list, start.year = 2024, batch = batch)
```

@@

```{r}
SF12.change.by.deciles(int.list, scen.list, batch = batch)
```

@@

SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic', batch = batch)
SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one', batch = batch)
SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children', batch = batch)
SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25', batch = batch)
#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled', batch = batch)
